Free surface computations in mantle convection models

### 2015-07-10 free-surface-paper.tex
Edit
Insert figure
Add figure for convergence of quasi-implicit scheme

Indeed, if we discretize the Stokes system with the quasi-implicit stabilization term, we find
a new generalized eigenvalue problem:

@@

\section{Results}
\begin{itemize}
\item Crameri benchmarks
\item comparison between stabilization schemes (stability)
\item comparison between stabilization schemes (accuracy)
\end{itemize}
\section{Discussion}

>>>>

If we discretize the Stokes system with the quasi-implicit stabilization term, we find
a new generalized eigenvalue problem:

@@

\section{Results}

\begin{figure*}
\includegraphics[width=0.9\textwidth]{figures/timestep_convergence.pdf}
\caption{Convergence test with timestep size.}
\label{fig:timestep_convergence}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.9\textwidth]{figures/timestep_convergence_qi.pdf}
\caption{Convergence test with timestep size, quasi-implicit}
\label{fig:timestep_convergence_qi}
\end{figure*}

\begin{itemize}
\item Crameri benchmarks
\item comparison between stabilization schemes (stability)
\item comparison between stabilization schemes (accuracy)
\end{itemize}
\section{Discussion}
